Generating the Blueprints of the Java Ecosystem

### 2015-02-28 msr.tex
fixed bad caption
Section 4 - pass

\begin{table}
\centering
\caption{Method Design Metrics}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Package Design}}}\\
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

@@

The measurements provided by this dataset, can be used both by researchers and practitioners to validate their ideas. Researchers can use the data to experiment with new quality models, or just validate them in real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.

The dataset includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}. These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns \cite{KARA14}.

In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations, since these dataset also analysed projects from the Maven repository.

>>>>

\begin{table}
\centering
\caption{Package Design Metrics}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Package Design}}}\\
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

@@

The measurements provided by our dataset, can be used by researchers and practitioners alike. Researchers can use the data to experiment with new quality models, or validate them in real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.

The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}. These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.

Finally, our dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations. This is because their datasets were also produced by analyzing projects coming from the Maven repository.
